\pkg{Rgbp}: Bayesian Hierarchical Modeling and Frequentist Method Check

### 2013-04-07 jss/article.tex
journal writing

The other model justification process is the method check.
\subsection{Pseudo-data Generation Process}
\subsection{Unbiased Coverage Probability}
\subsection{Rao-Blackwellized Coverage Probability}
\section[Example]{Example}
\subsection[Known Prior Mean]{Known Prior Mean}
Using 10 hospital data with PR
\subsection[Unknown Prior Mean and No Covariate]{Unknown Prior Mean and No Covariate}
Using 8 school data with GR
\subsection[Unknown Prior Mean and One Covariate]{Unknown Prior Mean and One Covariate}
Using 18 baseball data with BR

>>>>

Once we are sure that the hierarchical modeling can add a huge value on our research, the next natural quetsion will be about the validity of interval estimates. ``Does the confidence interval obtained via this Bayesian model-fitting process achieve pre-specified 100($1-\alpha$)\% confidence level for any true parameter values?'' Our answer is ``yes'' and \pkg{Rgbp} has a function to assure this point.

\subsection{Pseudo-data Generation Process}
\subsection{Unbiased Coverage Probability}
\subsection{Rao-Blackwellized Coverage Probability}
\section[Example]{Example}
\subsection[Known Prior Mean]{Known Prior Mean}
Using 10 hospital data with PR
\subsection[Unknown Prior Mean and No Covariate]{Unknown Prior Mean and No Covariate}
Using 8 school data with GR
\subsection[Unknown Prior Mean and One Covariate]{Unknown Prior Mean and One Covariate}
Using 18 baseball data with BR
